Smoking and COVID Living Review (v7): a bayesian analysis

### 2020-09-02 reports/bayesian_report.Rmd
updated for v7 final

``` {r excluding_studies}
exclude_from_analysis <- c('isaric_1', 'isaric_2', 'isaric_3', 'miyara_old', 'isaric_4', 'mehra', 'hopkinson', 'gaibazzi', 'miyara_updated', 'russell_old', "petrilli_old", "magagnoli_old", "niedzwiedz_old", "bello_chavolla_old", "kimmig_old", "russell_old", "zuo_zuo_old", "patel_old", "shi_zuo_old")
```
We don't want to remove studies from the dataset despite them no longer being included in the analysis. The excluded studies are defined in this chunk of code. We have excluded this version the following studies:
-`r knitr::combine_words(exclude_from_analysis)`
Generally we label these as _old in the Google sheet but there are exceptions to this so we manually define them at the moment.

@@

included_studies <- quality_table_2 %>%
  filter(overall_quality != 'poor') %>%
  select(lead_author) %>%
  filter(lead_author != "reiter")

>>>>

``` {r excluding_studies}
exclude_from_analysis <- c('isaric_1', 'isaric_2', 'isaric_3', 'miyara_old', 'isaric_4', 'mehra', 'hopkinson', 'gaibazzi', 'miyara_updated', 'russell_old', "petrilli_old", "magagnoli_old", "niedzwiedz_old", "bello_chavolla_old", "kimmig_old", "russell_old", "zuo_zuo_old", "patel_old", "shi_zuo_old", "riley_old")
```
We don't want to remove studies from the dataset despite them no longer being included in the analysis. The excluded studies are defined in this chunk of code. We have excluded this version the following studies:
-`r knitr::combine_words(exclude_from_analysis)`
Generally we label these as _old in the Google sheet but there are exceptions to this so we manually define them at the moment.

@@

included_studies <- quality_table_2 %>%
  filter(overall_quality != 'poor') %>%
  select(lead_author) %>%
  filter(!lead_author %in% c("reiter", "hippisley_cox"))
